Creative Destruction in the Philosophy of Technology

### 2016-05-09 encryption/paper.tex
asdf

\subsubsection{National Security}
Many arguments for regulating encryption focus on the fact that weaker encryption would aid national security efforts.
This argument is difficult to address for various reasons.
However, I recall hearing that Snowden revealed that little to none of the NSA's privacy-invading efforts had contributed to national security.
And that many of the privacy breaches were justified under the guise of national security, but in fact had other uses and purposes.
To me, this debate in part boils down the efficacy.
There is some sweet spot where privacy and national security are optimized, but the public does not have adequate information to truly assess this problem, as we do not details about national security efforts or privacy invasion.

>>>>

\subsubsection{National Security}
Many arguments for regulating encryption focus on the fact that strong encryption helps criminals undermine national security efforts.
This argument is difficult to address for various reasons.
However, I recall hearing that Snowden revealed that little to none of the NSA's privacy-invading efforts had contributed to national security.
And that many of the privacy breaches were justified under the guise of national security, but in fact had other uses and purposes.
To me, this debate in part boils down the efficacy.
There is some sweet spot where privacy and national security are optimized, but the public does not have adequate information to truly assess this problem, as we do not details about national security efforts or privacy invasion.

\section{Summing it up}
The last section, instead of providing a clear answer to question of encryption, brought up some important points that need to be addressed in order to come to satisfying answer.
The aim of this section is to highlight those points, as they should be useful to future work.

The first point is that sending messages over the internet is different from talking.
When people communicate via the internet, the messages are publicly accessible (to some extent), since they bounce from server to server on their way to their destination.
Talking on the internet is fundamentally different from two parties talking in a private room; rather, they are talking in a crowded room.
Then, the only possible method by which the parties can achieve privacy is by using public-key encryption, but we must first ask the question: do people have a right to a private conversation in a crowded room? 
In a real world, non-internet setting, I'm inclined to say no. 
By trying to have a conversation in a crowded room, the parties would inconvenience others, for example by requiring that others steer clear of the section of the room in which the parties are conversing.
But what if the parties do not inconvenience anyone when having their conversation?
Encryption on the internet does not inconvenience those with whom the parties am not communicating.
My conclusion is that there is no easy way to compare encryption to talking.
At any point, there are differences such that we, as philosophers, lose the ethical importance of the matter when we try to draw parallels.

The second point is really a sub-problem that needs to be addressed to resolve the encryption question.
The sub-problem asks, ``do the institutions that run the internet have the right to read the contents of the messages they are handling?''
In section 3.0.3 I introduced formal notation for what it means to send a message $x$ over the internet.
When a message is sent over the internet, we put the internet into an envelope, creating $l(x)$, such that for the handlers of the internet to read the message they need to open the envelope.
In the real world, opening the envelope could take many forms; for example, the handlers of the internet could simply save the message after they process it; such an action is above and beyond the duty of the runners of the internet - they do not need to save the message to perform their job, and it doesn't even help them perform their job better - so we should consider such an action as not required.
This sub-problem is can likely be addressed by appealing to business ethics: to what extent can a business investigate the input to a request from a client without violating the client's privacy?

The third point is that national security is an important consideration.
Undoubtedly, the internet and encryption could be used to organize events that we have a moral responsibility to prevent, if it is within our power.
This question ultimatley asks how do we balance the trade-off between national security and privacy.
Many parties from many perspectives have different beliefs on this question, and I imagine that the problem will continue to be contentious for years to come.

%
%- Sending messages over the internet is different from talking.
%    - Same room private conversation
%    - Same public conversation
%- Does a business or government have the right to open an envelope?
%    - Goes back to business ethics and what is infrastructure
%- National security
%    - At what point do we have unequivocal right to privacy that trumps any national security argument?

\section{Conclusion}
We need to address many other problems before we can come to a good understanding and conclusion to whether we have a right to use encryption over the internet.
The aim of this paper was to start a formal process for thinking through the question.
Another easy step forward is see how the arguments for and against encryption fall into the tropes of new and emerging science technology (NEST) ethics.
We refer the reader to \cite{nest}, a good overview of NEST ethics and common responses.
